---
title: "Available Datasets"
output: word_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
df <- read_csv("data/datasets.csv")
```

# Context

Below is a list of public datasets which are available at county, tracts and/or address level.  While there are many more datasets available at the county level, these allow for 'zoom-in' visibility from state to county to census tract.

# Datasets

This list includes datasets which are available at one or more of the following levels of aggregation:

- Address (*allows for geocoding and attribution of location to census tract*)
- Census Tract
- County

These lower levels of aggregation can be rolled up to state level using FIPS codes.

The list of datasets are tracked in the `.csv` file located in the data folder, with more specific documentation found below as issues are identified.  Please push a commit marking the `complete` field in the .csv file as `TRUE`.  There are currently `r sum(df$complete)` datasets completed for inclusion.

```{r echo=FALSE}
df %>%
  mutate(
    datalink = paste0("[",dataset,"](",docs,")"),
    county = if_else(!is.na(county),paste0("[x](",county,")"),""),
    tract = if_else(!is.na(tract),paste0("[x](",tract,")"),""),
    address = if_else(!is.na(address),paste0("[x](",address,")"),""),
  ) %>%
  select(topic,datalink,publisher,county,tract,address) %>%
  arrange(topic) %>%
  knitr::kable()
```

