---
title: "readme"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
df <- read_csv("docs/datasets.csv")
```

**Under active development; not ready for use**

# Purpose

This repository contains scripts for reading, transforming and combining datasets that are relevant for analysis of behavioral health and social determinants of health (SDoH) at the local neighborhood level (using 'census tract' as a proxy for 'neighborhood') and, where necessary, county level.  

# Datasets

This list includes datasets which are available at one or more of the following levels of aggregation:

- Address (*allows for geocoding and attribution of location to census tract*)
- Census Tract
- County

These lower levels of aggregation can be rolled up to state level using FIPS codes.

The list of datasets are tracked in the `.csv` file located in the data folder, with more specific documentation found below as issues are identified.  Please push a commit marking the `complete` field in the .csv file as `TRUE`.  There are currently `r sum(df$complete)` datasets completed for inclusion.

```{r echo=FALSE}
df %>%
  mutate(
    datalink = paste0("[",dataset_name,"](",docs,")"),
    county = if_else(!is.na(county),paste0("[x](",county,")"),""),
    tract = if_else(!is.na(tract),paste0("[x](",tract,")"),""),
    address = if_else(!is.na(address),paste0("[x](",address,")"),""),
  ) %>%
  select(topic,datalink,publisher,county,tract,address) %>%
  arrange(topic) %>%
  knitr::kable()
```

# Processing and Format

There are different output file formats for each level of aggregation in the data.

## Census Tract Dataset

The following fields must be included in all files:

- `dataset`: A shortened name of the dataset, to allow for subsetting when datasets are combined.
- `state`: Two-digit state 2010 FIPS code
- `county`: Three-digit county 2010 FIPS code
- `tract`: Six-digit tract 2010 FIPS code 
- `year`: The year of the published dataset.
- `race`: Should be marked as `pooled` where data is not broken out by race.  Should be marked as `NA` when the variable is not related to a population metric, such as in a count of facilities.
- `gender`: Should be marked as `pooled` where data is not broken out by gender.  Should be marked as `NA` when the variable is not related to a population metric, such as in a count of facilities.
- `age_range`: Should be marked as `pooled` where data is not broken out by age range. Should be marked as `NA` when the variable is not related to a population metric, such as in a count of facilities.
- `var_name`: The name of the variable/metric being reported.
- `value`: The numeric value of the measure identified in `var_name`
- `stat_type`: The type of summary statistic being reported in `value`.  For example: `n`, `mean`, `se`, `median`, etc.

## County-level Dataset

All fields from the census tract level data should be included in all files, other than the `tract` variable.

## Address Dataset

Address-level datasets should include the following fields:

- `dataset`: A shortened name of the dataset, to allow for subsetting when datasets are combined.
- `state`:
- `county`:
- `tract`: The census tract within which the address is located, obtained by using the `TBDfun::census_tract` function.
- `address`:
- `lat`, `lon`: Geocoded latitude and longitude coordinates of `address`
- `year`: The year of the published dataset.
- `...`: Other variables specific to the dataset, which may be of value to retain, though these will not be aggregated in the tract or county-level data.

# Variables

A list of available variables in the combined datasets are available in [the data dictionary](https://github.com/j-hagedorn/locals/blob/master/docs/data_dictionary.csv).
